### 2020-03-28 Thesis-Chapter2-Background.tex
Add reading sources; update background

Two developments sewed the seeds for the Second Crypto War. The first was actually a non-development: when the Clinton
administration changed its encryption policy, the U.S. House dropped the SAFE Act \cite{kehl_right_2015}. This meant
that rather than being written in the pen of law, encryption policy was written in the pencil of executive order. The
second development was the events of and reaction to morning of September 11, 2001.

Three developments have triggered the Second Crypto War.
\begin{enumerate}
    \item The 2013 Snowden revelations
    \item The mid-2010s spread of default device encryption in smartphones
    \item The late-2010s spread of default E2E encryption in messaging services
\end{enumerate}

@@

The following laws and regulations have been applied to cases involving cryptography and access to encrypted
information:

\begin{itemize}
    \item The All Writs Act \cite{congress_1789}
    \item The Bill of Rights: Amendments I, IV, and V \cite{madison_1791}
    \item The Arms Export Control Act (AECA) of 1976 established export controls over strong encryption techniques
        introduced ITAR (International Traffic in Arms Regulations) \cite{morgan_hr13680_1976} \cite{kehl_right_2015}
    \item The Computer Fraud and Abuse Act (CFAA) of 1986 \cite{hughes_hr4718_1986} \cite{wolff_computer_2016}
    \item The Communications Assistance for Law Enforcement Act (CALEA) of 1994 \cite{edwards_hr4922_1994}
    \item \dots
\end{itemize}

@@

\begin{itemize}
    \item Australia: in 2018 passed its Assistance and Access bill \cite{ag_2018} \cite{newman_2018}
    \item UK: Investigatory Powers Act \cite{legislature_2016}
    \item EU: GDPR
    \item China: \cite{donahue_comparative_2018}
    \item Israel: \cite{donahue_comparative_2018}
    \item Japan, Korea? -- can't find anything
    \item \dots
\end{itemize}

>>>>

Two developments sewed the seeds for the Second Crypto War. The first was actually a non-development: when the Clinton
administration changed its encryption policy, the U.S. House dropped the SAFE Act \cite{kehl_right_2015}. This meant
that rather than being written in the pen of law, encryption policy was written in the pencil of executive order. The
second development was the events of and reaction to the morning of September 11, 2001. (resources on 9/11:
\cite{shamsi_2011}, \cite{bloss_escalating_2007}.)

Three developments have triggered the Second Crypto War.
\begin{enumerate}
    \item The 2013 Snowden revelations \cite{thorsen_cryptic_2017} \cite{treguer_us_2018}
    \item The mid-2010s spread of default device encryption in smartphones \cite{treguer_us_2018}
    \item The late-2010s spread of default E2E encryption in messaging services \cite{treguer_us_2018}
\end{enumerate}

@@

The following laws and regulations have been applied to cases involving surveillance, cryptography, and access to
encrypted information:

\begin{itemize}
    \item The All Writs Act \cite{congress_1789}
    \item The Bill of Rights: Amendments I, IV, and V \cite{madison_1791}
    \item The Arms Export Control Act (AECA) of 1976 established export controls over strong encryption techniques
        introduced ITAR (International Traffic in Arms Regulations) \cite{morgan_hr13680_1976} \cite{kehl_right_2015}
    \item Foreign Intelligence Surveillance (FISA) Act \cite{rodino_1978}
    \item The Computer Fraud and Abuse Act (CFAA) of 1986 \cite{hughes_hr4718_1986} \cite{wolff_computer_2016}
    \item Electronic Communications Privacy Act (ECPA) of 1986 \cite{kastenmeier_hr4952_1986}
    \item The Communications Assistance for Law Enforcement Act (CALEA) of 1994 \cite{edwards_hr4922_1994}
    \item Uniting and Strengthening America by Providing Appropriate Tools Required to Intercept and Obstruct Terrorism
        (USA PATRIOT ACT) Act of 2001 \cite{sensenbrenner_2001}
    \item FISA Amendments Act of 2008 \cite{reyes_hr6304_2008}
    \item Uniting and Strengthening America by Fulfilling Rights and Ensuring Effective Discipline Over Monitoring
        (USA FREEDOM) Act of 2015 \cite{sensenbrenner_2015}
    \item \dots
\end{itemize}

@@

\begin{itemize}
    \item Australia: in 2018 passed its Assistance and Access bill \cite{ag_2018} \cite{newman_2018}
    \item UK: Investigatory Powers Act \cite{legislature_2016}
    \item EU: GDPR
    \item China: \cite{donahue_comparative_2018}
    \item Israel: \cite{donahue_comparative_2018}
    \item Japan, Korea? -- can't find anything
    \item \dots General, see \cite{budish_encryption_2018}
\end{itemize}

### 2020-03-28 Thesis-Chapter5-PathsAhead.tex
Add reading sources; update background

\begin{itemize}
    \item Reject EA until technical capabilities are ready \cite{varia_2018}
    \item Be forthcoming with data so that we know what to work on \cite{devlin_2018}
    \item Don't prescribe technical methods, but be clear about principles \cite{matyas_incommensurability_2018}
    \item Fund the research \cite{varia_2018}
\end{itemize}

>>>>

\begin{itemize}
    \item Reject EA until technical capabilities are ready \cite{varia_2018}
    \item Be forthcoming with data so that we know what to work on \cite{devlin_2018}
    \item Don't prescribe technical methods, but be clear about principles \cite{matyas_incommensurability_2018}
        (e.g., ECPA became outdated because was too tied to specific technology \cite{shamsi_2011})
    \item Fund the research \cite{varia_2018}
\end{itemize}
